---
output: pdf_document
---

# Code that reproduces and explains Table 2 within Cornwell er al. (in press) New Phytologist

This code will load and reproduce the data in the tables for Cornwell et al. For more details see the [github repository](https://github.com/cornwell-lab-unsw/gymnoLitterFires).

Before we start we have to load a few packages and utility functions:

```{r}
source("load_data.R")
library(heplots)
```

## Load data

Then we can load the data.  The data in the tables comes from the litter size manipulation experiment.  

```{r}
alba<-process.data.manipulation("fire_littersize_manipulation_data.txt")
```

It's called alba because Alba Elvira (co-author and Erasmus student from University of Barcelona) managed these meso-scale burns.  

##Statistical analysis

These are mostly standard linear models.  Within the paper we report the significance of each factor and a measure of effect size see Cohen (1992).

### Max temperature
```{r}
maxtemp.mod<-lm(maxtemp~species*size,data=alba)
etasq(maxtemp.mod,anova=T)
```

### Temp sum
```{r}
temp.sum.mod<-lm(temp.sum~species*size,data=alba)
etasq(temp.sum.mod,anova=T)
```

### Fire front speed
```{r}
front.speed.mod<-lm(speed.to.sensors~species*size,data=alba)
etasq(front.speed.mod,anova=T)
```

### Total burning time
```{r}
total.burning.time.mod<-lm(total.burning.time~species*size,data=alba)
etasq(total.burning.time.mod,anova=T)
```

### Proportion of sample burned

Becasue this response variable is a proportion, we use a logit link function (using a logit link with proportion data throws a warning in R, but see discussion of this issue in Warton and Hui 2011).

```{r}
options(warn=-1)
alba$prop.b<-alba$percent.sample.burned/100
prob.burned.mod<-glm(prop.b~species*size,data=alba,family=binomial(logit))
etasq(prob.burned.mod,anova=F,test="F")
anova(prob.burned.mod,test="Chisq")
```
